Impacts of Social Backgrounds on People's Perception of the Risk of Getting AIDS

### 2022-04-11 outputs/paper/paper.Rmd
Update paper.Rmd

---
title: "Impacts of Social Backgrounds on People's Perception of the Risk of Getting AIDS"
subtitle: "An Analysis Based on the Kenya's Demographic and Health Survey in 1998"
author: 
  - Charles Lu
  - Mahak Jain
  - Yujun Jiao
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "Using data extracted from Kenya’s Demographic and Health Surveys in 1998, this analysis aims to study the Kenyans’ perception of their risk of getting AIDS. By analyzing the age, number of sex partners, province, and education of the survey’s participants, results show that these factors all have different levels of impact on people’s risk of being infected. R [@citeR] is used in this report to create visualizations for the results. In the future, this report can help scholars to dive deeper into the history of the sexually-transmissible disease, study the correlation between the transmission rate and social backgrounds, and aid the authorities in making governmental or health-related plans. "
header-includes:
  - \usepackage{placeins}
output:
  bookdown::pdf_document2:
    latex_engine: xelatex
    toc: true
    fig_caption: yes
bibliography: references.bib
thanks: "https://github.com/R300G/paper4_placeholder_name"
---

@@

While advocating changes to future health-related plans, it's also important to look back into the past to study the people's reactions, perceptions, and responses to similar matters in the past century. In the Kenya Demographic and Health Survey conducted in 1998, survey answers were collected to reflect the demographic, health, and living conditions of the average Kenyans[@DHS]. More precisely, this report extracts data from chapter 10 of the survey report, where Aids and other sexually transmitted diseases were discussed in detail. By using a data set taken and cleaned from two tables titled "AIDS-related knowledge," this report aims to analyze the impacts of genders, age groups, number of sexual partners, provinces and education levels on people's perception of the risk of getting AIDs. In other words, this report analyzes the question: what are the chances of getting AIDS for people from different backgrounds? This report utilizes analytic programming language R [@citeR]. R packages tidyverse [@tidyverse], janitor [@janitor] and dplyr [@dplyr] are used to clean, organize and manipulate the data. Furthermore, R packages ggplot2 [@ggplot2], scales [@scales] and knitr [@knitr] are used to create figures and tables. R packages bookdown [@bookdown] and tinytex [@tinytex] are used to generate the R markdown Report.

@@

Data used in this paper is extracted from table 10.9.1: Perception of the risk of getting AIDS: women and table 10.9.2 Perception of the risk of getting AIDS: men from the Kenya Demographic and Health Survey 1998 report [@DHS]. These two tables illustrate the female and male populations’ perceptions of their risk of getting the AIDS virus. Based on the tables, the independent variables include genders, age groups, marital status, number of sexual partners other than spouse, residence, province, and education. This report focuses on five variables from the data set: the gender, age, number of sexual partners, province and education. The marital status and residence are dropped. To sum up, all these five variables are analyzed in this report, and their impacts on the response variable, people’s perception of the risk of getting AIDS, are discussed.

@@

>>>>

---
title: "Impacts of Social Backgrounds on People's Perception of the Risk of Getting AIDS"
subtitle: "An Analysis Based on the Kenya's Demographic and Health Survey in 1998"
author: 
  - Charles Lu
  - Mahak Jain
  - Yujun Jiao
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "Using data extracted from Kenya’s Demographic and Health Surveys in 1998, this analysis aims to study the Kenyans’ perception of their risk of getting AIDS. By analyzing the age, marital status, number of sex partners, residence, province, and education of the survey’s participants, results show that these factors all have different levels of impact on people’s risk of being infected. R [@citeR] is used in this report to create visualizations for the results. In the future, this report can help scholars to dive deeper into the history of the sexually-transmissible disease, study the correlation between the transmission rate and social backgrounds, and aid the authorities in making governmental or health-related plans. "
header-includes:
  - \usepackage{placeins}
output:
  bookdown::pdf_document2:
    latex_engine: xelatex
    toc: true
    fig_caption: yes
bibliography: references.bib
thanks: "https://github.com/R300G/paper4_placeholder_name"
---

@@

While advocating changes to future health-related plans, it's also important to look back into the past to study the people's reactions, perceptions, and responses to similar matters in the past century. In the Kenya Demographic and Health Survey conducted in 1998, survey answers were collected to reflect the demographic, health, and living conditions of the average Kenyans[@DHS]. More precisely, this report extracts data from chapter 10 of the survey report, where Aids and other sexually transmitted diseases were discussed in detail. By using a data set taken and cleaned from two tables titled "AIDS-related knowledge," this report aims to analyze the impacts of genders, age groups, marital status, number of sexual partners, residence regions, provinces and education levels on people's perception of the risk of getting AIDs. In other words, this report analyzes the question: what are the chances of getting AIDS for people from different backgrounds? This report utilizes analytic programming language R [@citeR]. R packages tidyverse [@tidyverse], janitor [@janitor] and dplyr [@dplyr] are used to clean, organize and manipulate the data. Furthermore, R packages ggplot2 [@ggplot2], scales [@scales] and knitr [@knitr] are used to create figures and tables. R packages bookdown [@bookdown] and tinytex [@tinytex] are used to generate the R markdown Report.

@@

Data used in this paper is extracted from table 10.9.1: Perception of the risk of getting AIDS: women and table 10.9.2 Perception of the risk of getting AIDS: men from the Kenya Demographic and Health Survey 1998 report [@DHS]. These two tables illustrate the female and male populations’ perceptions of their risk of getting the AIDS virus. Based on the tables, the independent variables include genders, age groups, marital status, number of sexual partners other than spouse, residence, province, and education. This report focuses on all the variables from the data set: the gender, age, marital status, number of sexual partners, residence region, province and education. To sum up, all these variables are analyzed in this report, and their impacts on the response variable, people’s perception of the risk of getting AIDS, are discussed.

@@

## What is something we learn about the world?
